### 2016-11-03 capability-machine.tex
.

\begin{align*}
  \erase{W}{S} \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \undefined & \text{otherwise}
  \end{cases}
\end{align*}

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq (\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\exists \start,\addrend \ldotp s = (\start,\addrend) \land \\
      &\quad \dom(\hs) = [\start,\addrend] \land \\
      &\quad \forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\hat{W})
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\exists \start,\addrend \ldotp s = (\start,\addrend) \land \\
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\hat{W}}) %Does it make sense to use revokeTemp here when it does not "match up" with the world?
    \end{aligned}
  \right\}
\end{align*}

@@

\begin{align*}
    & \writeCond{}(\iota,\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nequal[n-1] \iota_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}

>>>>

\begin{align*}
  \erase{W}{S} \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\exists \start,\addrend \ldotp s = (\start,\addrend) \land \\
      &\quad \dom(\hs) = [\start,\addrend] \land \\
      &\quad \forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\hat{W})
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\exists \start,\addrend \ldotp s = (\start,\addrend) \land \\
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\hat{W}})
    \end{aligned}
  \right\}
\end{align*}
\lau{In the above $H$ definitions, $\hat{W}$ is not a world, so there is a type problem that needs to be fixed. Maybe solve the recursive domain equations wrt the worlds instead.}

@@

\begin{align*}
    & \writeCond{} : ((\Views \rightharpoonup \Regions) \times \Globals) \fun (\Addrs^2 \times \Worlds) \monnefun \DCPred{\nats}  \\
    & \writeCond{}(\iota,\gl)(\start,\addrend,W) =  \\
    & \quad \begin{aligned}[t]
              \{ n \mid & \;\exists r \in \var{localityReg}(g) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nequal[n-1] \iota_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}
